---
title: "Preregs"
author: "Jonas Rafi"
date: "13 mars 2018"
output: html_document
---



```{r setup, include = FALSE}

library(tidyr)
library(ggplot2)
```

# Pre-registration of published study protocols in two journals: a crude comparison
## Aim
Comparing the yearly amount of pre-registered study protocols in two journals.

## Overview
The journals BMJ Open and Trials invites authors to publish study protocols. Both of them have guidelines stating that pre-registration information should be included in the abstract under the heading "Trial registration". However, [BMJ Open](http://bmjopen.bmj.com/pages/authors/#study_protocols) enforces pre-registration for all study protocols, whereas [Trials](https://trialsjournal.biomedcentral.com/submission-guidelines/preparing-your-manuscript/study-protocol) acknowledge that pre-registration is necessary for health care interventions on human subjects. 

## Method
Using Scopus web-search to find the number of published study protocols for BMJ Open and Trials, with and without the string "registration" in the abstract. At first I tried with the package ["rscopus"](https://github.com/muschellij2/rscopus), but I wasn't able to connect to the Scopus API.

### Search criteria used to gather data on publication numbers:  

* ISSN("1745-6215") AND TITLE("Study protocol")  
* ISSN("1745-6215") AND TITLE("Study protocol") AND ("registration")  
* ISSN("2044-6055") AND TITLE("Study protocol")  
* ISSN("2044-6055") AND TITLE("Study protocol") AND ("registration")  

The number of publications for the years 2012-2017 was typed directly into this RMD-file. 2012 was set as starting year due to the low amount of prior publications in BMJ Open.

### Entering the data into R

``` {r}
data <- data.frame(year = c(2017, 2016, 2015, 2014, 2013, 2012, 2017, 2016, 2015, 2014, 2013, 2012),
                   journal = c(rep("BMJ Open", 6), rep("Trials", 6)),
                   total = c(204, 183, 97, 83, 42, 22, 461, 442, 456, 391, 333, 162),
                   reg = c(97, 57, 37, 47, 10, 6, 421, 378, 331, 323, 283, 151)
                   )

data$prop <- data$reg / data$total
```

## Results

``` {r}
ggplot(data, aes(x = year, y = prop)) +
        geom_point(aes(color = journal)) +
        geom_line(aes(color = journal)) +
        ylim(0,1)
```

Despite having a more flexible approach to pre-registration, Trials seem to have a higher proportion of published study protocols mentioning trial registration in their abstracts.

## Discussion

Despite the aim of this short assignment, the findings should not be used to infer anything about the actial proportions of pre-registered study protocols. I have not performed any controls on the data to see if my search queries work as intended.

## Conclusion

The conclusion is to not draw any conclusions based on this information.